\documentclass[aspectratio=169,xcolor=dvipsnames]{beamer}
\usetheme{Simple}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}



\title[short title]{Bridging the Gap: Analyzing Auction Prices and Day-Ahead Market Discrepancies at the Swiss-German Electricity Border}

\author{Nicolas Greber, Massimo Nardo, Vansh Khanna}
\institute
{
    Department of Finance \\
    University of Zurich
    \vskip 3pt
}
\date{\today}



\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Overview}
    % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
    \tableofcontents
    \section{Motivation}

\section{Data}

\section{Methodology}

\section{Results}

\section{Discussion}

\end{frame}

\begin{frame}{Motivation}

\begin{itemize}
    \item Switzerland is not part of the European Market Coupling system.
    \item Electricity trading occurs explicitly across Switzerland-Germany borders.
    \item Study focus:
    \begin{itemize}
        \item Analyze whether border prices reflect market price differences.
        \item Identify pricing error patterns if border prices fail to represent these differences.
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Data}
\begin{itemize}
    \item Day-Ahead Market Prices
    \begin{itemize}
        \item Data covers Switzerland, Germany-Luxembourg, and Germany-Austria-Luxembourg.
        \item Dataset spans 2016-2023 (restricted to 2019-2023 for analysis).
        \item Settlement:
        \begin{itemize}
            \item Swiss market: 11:00 CET.
            \item Most European markets: 12:00 CET.
        \end{itemize}
        \item Prices determined via supply-demand curves.
    \end{itemize}

    \item Cross-Border Auction Prices
    \begin{itemize}
        \item Data from Joint Allocation Office (JAO).
        \item Auctions allocate transmission capacity for electricity delivery.
        \item Daily auctions finalize at 09:30 CET for next day.
        \item Each unit = 1 megawatt-hour (MWh).
        \item Data covers 2019-2023 (downloaded via JAO API).
    \end{itemize}

    \item Photovoltaic (PV) Data
    \begin{itemize}
        \item Sourced from Swiss Federal Office of Energy (SFOE).
        \item Includes yearly installed PV capacity and number of installations.
        \item Converted from Excel to CSV for analysis.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Methodology}
\textbf{Stationarity Test (ADF)}
\begin{itemize}
    \item Tests if $\delta_t$ is stationary (temporary deviations) or non-stationary (persistent inefficiencies).
    \item Hypotheses: 
    $H_0$: $\delta_t$ has a unit root; 
    $H_1$: $\delta_t$ is stationary.
\end{itemize}

\textbf{Mean Test (HAC Adjustment)}
\begin{itemize}
    \item Tests if $E[\delta_t] = 0$ (no systematic mispricing) or $\neq 0$ (persistent discrepancies).
    \item Newey-West HAC estimator adjusts for autocorrelation and heteroskedasticity.
\end{itemize}

\textbf{Autocorrelation Analysis}
\begin{itemize}
    \item Evaluates temporal dependencies in $\delta_t$ at lag 24 (one day).
    \item Autocorrelation: $\rho_{24} = \frac{\text{Cov}(\delta_t, \delta_{t-24})}{\text{Var}(\delta_t)}$.
\end{itemize}
    
\end{frame}

\begin{frame}{Methodology}
\textbf{Variance Trend Analysis}
\begin{itemize}
    \item \textbf{Goal}: Detect temporal trends in pricing variability (\(\hat{\delta_t}\)).
    \item \textbf{Model}: \(\sigma_t(\hat{\delta_t}) = \alpha + \beta t + \epsilon_t\), where \(\beta\) measures the trend.
    \item \textbf{Hypotheses}:
    \begin{itemize}
        \item \(H_0\): \(\beta = 0\), no trend.
        \item \(H_1\): \(\beta \neq 0\), significant trend.
    \end{itemize}
    \item \textbf{Implications}:
    \begin{itemize}
        \item \(\beta > 0\): Growing inefficiencies.
        \item \(\beta < 0\): Improved market alignment.
    \end{itemize}
\end{itemize}

\vspace{0.3cm}

\textbf{Variance Ratio Test}
\begin{itemize}
    \item \textbf{Goal}: Compare variability across two periods.
    \item \textbf{Formula}: \(F = \frac{\text{Var}_{\text{later}}}{\text{Var}_{\text{earlier}}} \sim F(n_1 - 1, n_2 - 1)\).
    \item \textbf{Hypotheses}:
    \begin{itemize}
        \item \(H_0\): Variances are equal.
        \item \(H_1\): Variances differ.
    \end{itemize}
    \item \textbf{Significance}: \(p < 0.05\) suggests variability has changed.
\end{itemize}    
\end{frame}


%------------------------------------------------
\end{document}